### 2019-10-01 budget.tex
Edits to budget text

\subsection{Expenses}
A conservative breakdown of conference expenses is outlined in Table ******* on page *******. Emphasizing some of the points shown in the table, all rooms hosted in the Union are provided to registered student organizations (such as ANS) free of charge, which allows us to save significantly on event space. Meals catered through the University catering service reflect a 6.25\% sales tax in the total cost which is not represented in the unit cost. Gratuity is neglected as it is forbidden under the catering service’s policies, allowing us to save cost on meals. 
Under our most conservative estimates for budget and revenue, the spending margin is found to be 4.13\%. While this margin is tight, we feel this is justified as several costs in the expenses, such as reimbursements, are left significantly inflated as compared with previous years. Adopting previous years’ estimates of \$60,000 for travel reimbursements leaves a spending margin of 21.6\%, matching that of the most austere contingency plans provided in previous years. 
Assuming maximum expenses and an attendance of 450 students, the total cost per student is estimated at \$501.63. This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative. Neglecting the cost of travel reimbursements, the average cost per student falls to \$276.63, at or below that estimated for previous years.

>>>>

\subsection{Expenses}
A conservative breakdown of conference expenses is outlined in Table ******* on page *******. Emphasizing some of the points shown in the table, all rooms hosted in the Union are provided to registered student organizations (such as ANS) free of charge, which allows us to save significantly on event space. Gratuity is omitted for all catering provided by the University Catering service, as the University is unable to accept gratuity on purchases. 
Under our most conservative estimates for budget and revenue, the spending margin is found to be 9.62\%. This margin is generous and in line with that allotted in previous years. Additionally, our budget calls for significantly higher student travel reimbursements than what where accounted for in previously proposed budgets. Reducing to levels proposed in recent years would free an additional $\$$ 40,000, if absolutely necessary. 
Assuming maximum expenses and an attendance of 450 students, the total cost per student is estimated at \$ 485.05. This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative. Neglecting the cost of travel reimbursements, the average cost per student falls to \$260.05, at or below that estimated for previous years.
